---
title: "Lab 02 - Plastic waste"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

```{r plastic-waste-continent}
ggplot(data = plastic_waste, 
       aes(x = plastic_waste_per_cap, fill = continent))+
  geom_histogram()+
facet_wrap (~continent, nrow = 3)+
labs(
  title = "Histogram"
)
```

Africa seems to have the lowest plastic waste per capita. North America have relatively higher plastic waste per capita compared to other continents.

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.5)+
  labs(
    title = "Density Plot"
  )
```

### Exercise 3
Color and fill are aesthetic of the plot because it adds extra elements into the plot. For example, without color/fill= continent, we will have single line instead of multiple lines that are drawn based on different continent. It's like adding eyes on a face.

Alpha, however, does not add extra elements but helps you to adjust the appearance of the plot. It's like adjusting the size of eyes on a face.
 

### Exercise 4


```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  labs(
    title = "Violin Plot"
  )
```

##### What do the violin plots reveal that box plots do not? What features are apparent in the box plots but not in the violin plots?

Violin plots show the shape of distributions of each continents, which box plots don't. But box plots clearly show the mean and SD, which violin plots don't.


### Exercise 5


```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste, 
                     y = plastic_waste_per_cap)) +
  geom_point()+
  labs(
    title="Scatter Plot for Plastic Waste and Mismanaged Plastic Waste"
  )
```

No clear pattern to indicate the relationship between plastic waste per capita and mismanaged plastic waste per capita.

### Exercise 6


```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste, 
                     y = plastic_waste_per_cap,
                     color = continent)) +
  geom_point()+
  labs(
    title="Scatter Plot for Plastic Waste and Mismanaged Plastic Waste",
    subtitle = "by continent"
  )
```

### Exercise 7


```{r plastic-waste-population-total}
ggplot(data = plastic_waste, 
       mapping = aes(x = total_pop, 
                     y = plastic_waste_per_cap)) +
  geom_point()+
  labs(
    title="Total Population and Plastic Waste Per Capita"
  )
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop, 
                     y = plastic_waste_per_cap)) +
  geom_point()+
  labs(
    title="Coastal Population and Plastic Waste Per Capita"
  )
```

None of these pairs of variables appear strong linear association.

### Exercise 8


```{r recreate-viz}
ggplot(data = plastic_waste %>%
         filter (plastic_waste_per_cap < 3),
       mapping = aes(x = coastal_pop/total_pop, 
                     y = plastic_waste_per_cap,
                     color = continent)) +
  geom_point()+
  scale_color_viridis_d()+
  stat_smooth(color = "black")+
  labs(
    x = "Coastal population proportion (Coastal / total population)",
    y = "Plastic Waste per capita",
    fill = "Continent",
    title="Plastic waste vs. coastal population proportion",
    subtitle = "by continent")+
theme_light()+
theme(
  panel.border = element_blank(),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey90"), 
  panel.grid.minor = element_line(size = 0.2, linetype = 'solid',
                                colour = "grey90")
)
```
